### 2022-05-24 paper.Rmd
this is not needed when file info is correctly stored
...same in the paper

## add information on simulation conditions
## TODO: use this and not the one during anticlustering computations
conditions <- info_from_filename_vectorized(df$file)
df <- subset(df, select = -c(N, M, SD))
df <- data.frame(df, conditions)

# Make long format
ldf <- pivot_longer(
  df,
  cols = paste0(c("kvar", "kmeans", "means", "sd", "skew", "kur", "cor"), "_obj"),
  names_to = "Objective",
  names_pattern = "(.*)_obj"
)

## Global results, aggregated across all simulation variables
tab <- ldf %>% 
  group_by(method, Objective) %>% 
  summarise(Mean = round(mean(value), 3)) %>% 
  filter(Objective %in% c("means", "sd", "skew", "kur", "cor")) %>% 
  pivot_wider(names_from = Objective, values_from = Mean) %>% 
  select(c(means, sd, skew, kur, cor))

@@

# Plot the results, by N
ldf %>% 
  group_by(method, Objective, N) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(
    Objective %in% c("means", "sd", "skew", "kur", "cor"),
    method != "random"
  ) %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>%
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16)

>>>>

# Make long format
ldf <- pivot_longer(
  df,
  cols = paste0(c("means", "sd", "skew", "kur", "cor"), "_obj"),
  names_to = "Objective",
  names_pattern = "(.*)_obj"
)

## Global results, aggregated across all simulation variables
tab <- ldf %>% 
  group_by(method, Objective) %>% 
  summarise(Mean = round(mean(value), 3)) %>% 
  pivot_wider(names_from = Objective, values_from = Mean) %>% 
  select(c(means, sd, skew, kur, cor))

@@

# Plot the results, by N
ldf %>% 
  group_by(method, Objective, N) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>%
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16)
